An Embedding Framework for the Design and Analysis of Consistent Polyhedral Surrogates

### 2023-06-15 poly-embed-journal/poly-embed-journal.tex

\raft{FYI: Added this paragraph since we needed it in \S~\ref{sec:poly-ie-consistency}}
Indirect elicitation is a weaker condition than calibration~\citep{steinwart2008support,agarwal2015consistent,finocchiaro2021unifying}; we briefly sketch the argument.
Suppose $L$ is minimizable and $(L,\psi)$ is calibrated with respect to $\ell$, and set $\Gamma=\prop{L}$ and $\gamma=\prop{\ell}$.
Let $u\in\reals^d$ and $p\in\Gamma_u$.
From eq.~\eqref{eq:calibrated}, if $\psi(u) \notin \gamma(p)$, then we would have $u\notin\Gamma(p)$, a contradiction to $p\in\Gamma_u$.
Thus, $\psi(u) \in \gamma(p)$, so $p\in\gamma_{\psi(u)}$.
In fact, indirect elicitation is strictly weaker; take hinge loss with the link $\psi(u) = -1$ for $u < 1$ and $\psi(u) = 1$ for $u\geq 1$.
\reviewerone{A}
\reviewerthree{A}
While this pair indirectly elicits the mode, we can show it is not calibrated with respect to 0-1 loss. 
Suppose $ p  = (0, 1)$ and consider the sequence $\{u_m\} = \{1 - \frac 1 {m+1}\}_{m=1}^\infty$, which limits to $1$, but $\psi(u_m) = -1$ for all $m$.
Therefore, the infimum of hinge loss over reports not linking to $1$ approaches the infimum over all reports.
\citet{agarwal2015consistent} were the first to formally connect property elicitation to calibration, though their results generally do not apply to discrete prediction tasks.

>>>>

\raft{FYI: Added this paragraph since we needed it in \S~\ref{sec:poly-ie-consistency}}
Indirect elicitation is a weaker condition than calibration~\citep{steinwart2008support,agarwal2015consistent,finocchiaro2021unifying}; we briefly sketch the argument.
Suppose $L$ is minimizable and $(L,\psi)$ is calibrated with respect to $\ell$, and set $\Gamma=\prop{L}$ and $\gamma=\prop{\ell}$.
Let $u\in\reals^d$ and $p\in\Gamma_u$.
From eq.~\eqref{eq:calibrated}, if $\psi(u) \notin \gamma(p)$, then we would have $u\notin\Gamma(p)$, a contradiction to $p\in\Gamma_u$.
Thus, $\psi(u) \in \gamma(p)$, so $p\in\gamma_{\psi(u)}$.
In fact, indirect elicitation is strictly weaker; take hinge loss with the link $\psi(u) = -1$ for $u < 1$ and $\psi(u) = 1$ for $u\geq 1$.
\reviewerone{A}
\reviewerthree{A}
While this pair indirectly elicits the mode, we can show it is not calibrated with respect to 0-1 loss. 
Suppose $p = (0, 1) \in \simplex$ is the distribution putting all weight on $y=1$, and consider any sequence $u_m \to 1$ with $u_m < 1$ for all $m$.
Then the loss approaches the Bayes optimal, $L(1)_1 = 0$, but $\psi(u_n) = -1$ for all $n$, violating calibration.
\citet{agarwal2015consistent} were the first to formally connect property elicitation to calibration.
